---
title: "Final Presentation"
author: "Jared Winslow"
date: "6-10-20"
output: 
  ioslides_presentation:
    smaller: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(dplyr)
library(ggplot2)
library(alr4)


# Import files
demographic <- read.csv("KKI_demographicInfo.csv")

movement <- read.csv("KKI_movementAssessmentBatteryforChildren.csv")

social <- read.csv("KKI_SocialResponsivenessScaleQuestionnaire.csv")


# Fix formatting
names(movement)[1] <- "ID"

names(demographic)[1] <- "ID"

names(social)[1] <- "ID"


# Join together data
almostdata <- full_join(demographic, social, by="ID")

data <- full_join(almostdata, movement, by=c("ID","visit"))


# Date cleaning

# Filter out duplicates
duplicates <- which(duplicated(data))

data <- data[-duplicates, ]

# Near duplicates removal by row (near duplicate meaning two entries with only difference being CurrentlyNotTakingMeds value)
data <- filter(data, ID != c(1056,1066,1222,1223,1268,1414,1444,1504,1540)) # ID: 1056, 1066, 1222, 1223, 1268, 1414, 1444, 1504, 1540 respectively 

# Filter out participants who didn't or couldn't follow directions
data <- filter(data, !(is.na(mABC_TotalStandardScore))) # ID: 1622
data <- filter(data, ID != c(2106,1341))
# Don't filter out participants who experienced minor difficulties (i.e. band-aid) ID: 2121, or participants who gave questionable effort (it is likely many children gave sub-par effort but it wasn't noted) ID: 2018


# Save entries with visit = 2 (or 3) for later
dataWithSecondVisit <- data
secondVisit <- filter(dataWithSecondVisit, visit==2 || visit==3) 

# Count by visit
countByVist <- summarize(group_by(dataWithSecondVisit, visit), count=n())

# Filter out repeat visits (no entries of repeat visits had a social deficit score)
data <- filter(data, visit==1)

# Filter out remaining entries without SRS score
data <- filter(data, !(is.na(SRS_TotalRawScore)))

# Make SRS_VERSION a factor
data$SRS_VERSION <- as.factor(data$SRS_VERSION)
```

## Research Question

Scientisits collected data on a variety of children's attributes, including gender, age, social deficit scores, intelligence score, handedness, and balance, dexterity, catching, & throwing abilities, which were aggregated to create a movement score. 

In looking at this data, we are interested in determing whether their is relationship between social deficit scores and movement ability, especially in regards to children with ADHD and autism. 

## The Data

Here are the demographics of our participants after filtering out repeat visits, other duplicates, and troublemakers:

```{r}
genderGroupCount <- summarize(group_by(data, Gender, PrimaryDiagnosis), Count=n())
```

        TypDev, ADHD, Autism
        63,     45,   25    Female
        170,    112,  118   Male



```{r}
# Densities for the variables SRS_TotalRawScore, mABC_TotalStandardScore, and mABC_AGE all look *relatively* normal.

# Densities
srsDensity <- ggplot(data) + geom_density(aes(SRS_TotalRawScore))

movementDensity <- ggplot(data) + geom_density(aes(mABC_TotalStandardScore))

ageDensity <- ggplot(data) + geom_density(aes(mABC_AGE))

# SRS score boxplots by primary diagnosis
srsBoxplot <- ggplot(data, aes(x=PrimaryDiagnosis, y=SRS_TotalRawScore, color=PrimaryDiagnosis)) + geom_boxplot()

# Movement score boxplots by primary diagnosis
movementBoxplot <- ggplot(data, aes(x=PrimaryDiagnosis, y=mABC_TotalStandardScore, color=PrimaryDiagnosis)) + geom_boxplot()

# Based on our initial plots, we are justified in stratifying the data by primary diagnosis group
typ <- filter(data, PrimaryDiagnosis=="None")

adhd <- filter(data, PrimaryDiagnosis=="ADHD")

autism <- filter(data, PrimaryDiagnosis=="Autism")

# So let's now look at each group individually

# Typically Developing
srsTypDensity <- ggplot(typ) + geom_density(aes(SRS_TotalRawScore))
movementTypDensity <- ggplot(typ) + geom_density(aes(mABC_TotalStandardScore))
ageTypDensity <- ggplot(typ) + geom_density(aes(mABC_AGE))

typScatterplot <- ggplot(typ, aes(x=mABC_TotalStandardScore, y=SRS_TotalRawScore, color=PrimaryDiagnosis)) + geom_point() + geom_jitter() + geom_smooth() + geom_smooth(method="lm", color="cyan")

# ADHD
srsADHDDensity <- ggplot(adhd) + geom_density(aes(SRS_TotalRawScore))
movementADHDDensity <- ggplot(adhd) + geom_density(aes(mABC_TotalStandardScore))
ageADHDDensity <- ggplot(adhd) + geom_density(aes(mABC_AGE))

adhdScatterplot <- ggplot(adhd, aes(x=mABC_TotalStandardScore, y=SRS_TotalRawScore, color=PrimaryDiagnosis)) + geom_point() + geom_jitter() + geom_smooth() + geom_smooth(method="lm", color="cyan")

# Autism
srsAutismDensity <- ggplot(autism) + geom_density(aes(SRS_TotalRawScore))
movementAutismDensity <- ggplot(autism) + geom_density(aes(mABC_TotalStandardScore))
ageAutismDensity <- ggplot(autism) + geom_density(aes(mABC_AGE))

autismScatterplot <- ggplot(autism, aes(x=mABC_TotalStandardScore, y=SRS_TotalRawScore, color=PrimaryDiagnosis)) + geom_point() + geom_jitter() + geom_smooth() + geom_smooth(method="lm", color="cyan")
```

And here is a preliminary visual of the relationship between social deficits and movement ability:

```{r fig.width=5, fig.height=2.5}
ggplot(data, aes(x=mABC_TotalStandardScore, y=SRS_TotalRawScore, color=PrimaryDiagnosis)) + geom_point() + geom_jitter() + geom_smooth(method="lm", color="cyan") + labs(x="Movement Score", y="SRS Score")
```

```{r}
# At first glance, there seems to be a strong relationship between social deficit score and movement score, but from looking at the colored primary diagnosis groups, much of this trend comes from group differences, meaning we should stratify the data by primary diagnosis group.

# After splitting up the data in this way and reviewing the scatterplots and densities of the same three variables, we see a much weaker relationship between the two variables for the typically developing and adhd groups and almost no relationship for the autism group. All the densities (nine of them) look *relatively* normal except social deficit score's.
```


## The Secret Influencer: SRS Version

The two versions of the social deficit test were not consistent with one another neither in general nor for the individual primary diagnosis groups, especially typically developing. From here on, we will stratify the data by test version.

```{r}
# Now let's look at these plots seperated by version number

ver1 <- filter(data, SRS_VERSION==1)
ver2 <- filter(data, SRS_VERSION==2)
typVer1 <- filter(typ, SRS_VERSION==1)
typVer2 <- filter(typ, SRS_VERSION==2)
adhdVer1 <- filter(adhd, SRS_VERSION==1)
adhdVer2 <- filter(adhd, SRS_VERSION==2)
autismVer1 <- filter(autism, SRS_VERSION==1)
autismVer2 <- filter(autism, SRS_VERSION==2)
```

```{r fig.width=2.5,fig.height=1.8}
# SRS score versus ID

# ggplot(data, aes(x=ID, y=SRS_TotalRawScore, color=SRS_VERSION)) + geom_point() + geom_jitter() + labs(title="SRS Scores and Test Version", x="ID", y="SRS Scores", color="Test Version") + theme(legend.position = "none")

ggplot(typ, aes(x=ID, y=SRS_TotalRawScore, color=SRS_VERSION)) + geom_point() + geom_jitter() + labs(title="Typically Developing", x="ID", y="SRS Score") + theme(legend.position = "none")

ggplot(adhd, aes(x=ID, y=SRS_TotalRawScore, color=SRS_VERSION)) + geom_point() + geom_jitter() + labs(title="ADHD", x="ID", y="SRS Score") + theme(legend.position = "none")

ggplot(autism, aes(x=ID, y=SRS_TotalRawScore, color=SRS_VERSION)) + geom_point() + geom_jitter() + labs(title="Autism", x="ID", y="SRS Score") + theme(legend.position = "none")
```

```{r fig.width=2.5, fig.height=2.2}
# ggplot(data, aes(x=mABC_TotalStandardScore, y=SRS_TotalRawScore, color=SRS_VERSION)) + geom_point(size=1) + geom_jitter() + geom_smooth(method="lm", color="green") + labs(title="SRS Score vs Movement Score", x="Movement Scores by Test Version", y="SRS Scores by P.D. Group") + facet_grid(vars(PrimaryDiagnosis), vars(SRS_VERSION))

ggplot(typ, aes(x=mABC_TotalStandardScore, y=SRS_TotalRawScore, color=PrimaryDiagnosis)) + geom_point() + geom_jitter() + geom_smooth(method="lm", color="cyan") + facet_grid(cols = vars(SRS_VERSION)) + labs(title="Typically Developing", x="Movement Score", y="SRS Score") + theme(legend.position = "none")

ggplot(adhd, aes(x=mABC_TotalStandardScore, y=SRS_TotalRawScore, color=PrimaryDiagnosis)) + geom_point() + geom_jitter() + geom_smooth(method="lm", color="cyan") + facet_grid(cols = vars(SRS_VERSION)) + labs(title="ADHD", x="Movement Score", y="SRS Score") + theme(legend.position = "none")

ggplot(autism, aes(x=mABC_TotalStandardScore, y=SRS_TotalRawScore, color=PrimaryDiagnosis)) + geom_point() + geom_jitter() + geom_smooth(method="lm", color="cyan") + facet_grid(cols = vars(SRS_VERSION)) + labs(title="Autism", x="Movement Score", y="SRS Score") + theme(legend.position = "none")
```

```{r}
# When we split up the data by primary diagnosis group and then compare the two versions, there are differences in the linear model lines.

# For the typically developing group, the means are different for the two versions; this explains the bimodal (non-normal) density we saw previously, i.e. the odd one out was not normal directly because of test version. If we check the densities seperately for each version we would see they are relatively normal.
```

## Controlling for Age and Sex

```{r}
# Comparing SRS scores by sex

# Scatterplot of SRS score versus movement score for male and female
female <- filter(data, Gender=="F")

male <- filter(data, Gender=="M")

# Not added to final presentation
genderScatterplot <- ggplot(data, aes(mABC_TotalStandardScore, SRS_TotalRawScore, color=Gender)) + geom_point() + geom_smooth(data=female, method="lm", color="red") + geom_smooth(data=male, method="lm", color="cyan")

# Almost the same line of best fit
```

The differences between sexes in terms of social deficits is minimal. Social deficit scores don't really change with age and movement scores increase with age. 

```{r fig.width=2.5, fig.height=1.8}
ggplot(typ, aes(Gender, SRS_TotalRawScore, color=Gender)) + geom_boxplot() + facet_grid(cols = vars(SRS_VERSION)) + labs(title="Typically Developing", x="Sex", y="SRS Score") + theme(legend.position = "none")

ggplot(adhd, aes(Gender, SRS_TotalRawScore, color=Gender)) + geom_boxplot() + facet_grid(cols = vars(SRS_VERSION)) + labs(title="ADHD", x="Sex", y="SRS Score") + theme(legend.position = "none")

ggplot(autism, aes(Gender, SRS_TotalRawScore, color=Gender)) + geom_boxplot() + facet_grid(cols = vars(SRS_VERSION)) + labs(title="Autism", x="Sex", y="SRS Score") + theme(legend.position = "none")
```

```{r}
# The reason the means between the sexes are different for test version 2 of the autism group may be because the sample for females in the this category was quite small, so there is room for relatively more noise
```

```{r}
# The connected line used below is draw by connecting the mean of each of the age groups (for all primary diagnosis groups) together (in purple)

dataRoundedAge <- data %>%
  mutate(RoundedAge = round(mABC_AGE))

meanAge <- summarize(group_by(dataRoundedAge, RoundedAge), MeanAge=mean(mABC_AGE), MeanMovementScore=mean(mABC_TotalStandardScore), MeanSRSScore=mean(SRS_TotalRawScore))

# It looks quite similar to the loess smoother (for all primary diagnosis groups) for each of the two scatterplots (SRS score ~ age and movement score ~ age)
```

```{r fig.width=3.2, fig.height=2.8}
# Comparing SRS scores by age

ggplot(dataRoundedAge, aes(x=mABC_AGE, y=SRS_TotalRawScore, color=PrimaryDiagnosis)) + geom_point(position = "jitter") + facet_grid(cols = vars(SRS_VERSION)) + labs(title = "SRS Score vs Age", x = "Age", y = "SRS Score") + geom_smooth(data=typ, method="lm") + geom_smooth(data=adhd, method="lm") + geom_smooth(data=autism, method="lm") + geom_line(data = meanAge, aes(x=MeanAge, y=MeanSRSScore), color="purple", size=.5) + theme(legend.position = "none")

# There seems to be no improvement in social deficit score by age

# Comparing movement scores by age

ggplot(dataRoundedAge, aes(x=mABC_AGE, y=mABC_TotalStandardScore, color=PrimaryDiagnosis)) + geom_point(position = "jitter") + facet_grid(cols = vars(SRS_VERSION)) + labs(title = "Movement Score vs Age", x = "Age", y = "Movement Score") + geom_smooth(data=typ, method="lm") + geom_smooth(data=adhd, method="lm") + geom_smooth(data=autism, method="lm") + geom_line(data = meanAge, aes(x=MeanAge, y=MeanMovementScore), color="purple", size=.5) + theme(legend.position = "none")

# Since, there seems to be slight improvement in movement score by age (graphs below), this can be checked:

x <- data$mABC_AGE
y <- data$mABC_TotalStandardScore
xbar <- mean(x)
ybar <- mean(y)
corxy <- cor(x,y)
sdx <- sd(x)
sdy <- sd(y)
beta1 <- corxy * sdy/sdx
beta0 <- ybar + beta1*xbar
yhat <- beta1*x + beta0
residual <- y - yhat
ageCorrelation <- corxy
ageBetaEstimate <- beta1

# Not added to final presentation
movementVSAgeResiduals <- qplot(x=yhat,y=residual) + geom_smooth() + labs(title = "Social Score ~  Age: Residuals", x = "Social Score Y Hat Values", y = "Residuals")

# Here is the print out of the statistics for movement ability's growth:

# Not added to final presentation
ageString <- sprintf("Movement Score vs Age : Correlation %s, Beta 1 Estimate %s", round(ageCorrelation * 100) / 100, round(ageBetaEstimate * 100) / 100)
```

## Controlling for Other Variables

Secondary Diagnosis (red = no, blue = yes)

```{r fig.width=4,fig.height=2.2}
# Secondary Diagnosis

# ADHD

# Yes and No
adhdSecondYes <- filter(adhd, SecondaryDiagnosis=="Yes")

adhdSecondNo <- filter(adhd, SecondaryDiagnosis=="No")

ggplot(adhd, aes(x=mABC_TotalStandardScore, y=SRS_TotalRawScore, color=SecondaryDiagnosis)) + geom_point() + geom_jitter() + geom_smooth(data=adhdSecondYes, method="lm") + geom_smooth(data=adhdSecondNo, method="lm") + facet_grid(cols = vars(SRS_VERSION)) + labs(title = "ADHD", x = "Movement Score", y = "SRS Score") + theme(legend.position = "none")

# Autism

# There were a few unknown secondary diagnoses
autismWithSecond <- filter(autism, !(is.na(SecondaryDiagnosis)))

autismWithSecond <- filter(autism, ID!=1843)

autismWithSecond <- filter(autism, SecondaryDiagnosis!="Unknown")

# Yes and No
autismSecondYes <- filter(autism, SecondaryDiagnosis=="Yes")

autismSecondNo <- filter(autism, SecondaryDiagnosis=="No")

ggplot(autismWithSecond, aes(x=mABC_TotalStandardScore, y=SRS_TotalRawScore, color=SecondaryDiagnosis)) + geom_point() + geom_jitter() + geom_smooth(data=autismSecondYes, method="lm") + geom_smooth(data=autismSecondNo, method="lm") + facet_grid(cols = vars(SRS_VERSION)) + labs(title = "Autism", x = "Movement Score", y = "SRS Score") + theme(legend.position = "none")
```

ADHD Subtype (red = combined, blue = inattentive, green = hyperactive/impulsive)

```{r fig.width=3.8,fig.height=2.2, warning=FALSE}
# ADHD Subtype

# ADHD

# The subtypes
adhdCombined <- filter(adhd, ADHD_Subtype=="Combined")

adhdInattentive <- filter(adhd, ADHD_Subtype=="Inattentive")

adhdHI <- filter(adhd, ADHD_Subtype=="Hyperactive/Impulsive")

ggplot(adhd, aes(x=mABC_TotalStandardScore, y=SRS_TotalRawScore, color=ADHD_Subtype)) + geom_point() + geom_jitter() + geom_smooth(data=adhdCombined, method="lm") + geom_smooth(data=adhdInattentive, method="lm") + geom_smooth(data=adhdHI, method="lm") + facet_grid(cols = vars(SRS_VERSION)) + labs(title = "ADHD", x = "Movement Score", y = "SRS Score") + theme(legend.position = "none")

# Autism

# Filter out autistic particpants without adhd
autismWithADHD <- filter(autism, !(is.na(ADHD_Subtype)))

autismWithADHD <- filter(autismWithADHD, ADHD_Subtype!="Missing DICA")

autismWithADHD <- filter(autismWithADHD, ADHD_Subtype!="No dx")

autismWithADHD <- filter(autismWithADHD, ADHD_Subtype!="")

# The subtypes                               
autismCombined <- filter(autism, ADHD_Subtype=="Combined")

autismInattentive <- filter(autism, ADHD_Subtype=="Inattentive")

autismHI <- filter(autism, ADHD_Subtype=="Hyperactive/Impulsive")

ggplot(autismWithADHD, aes(x=mABC_TotalStandardScore, y=SRS_TotalRawScore, color=ADHD_Subtype)) + geom_point() + geom_jitter() + geom_smooth(data=autismCombined, method="lm") + geom_smooth(data=autismInattentive, method="lm") + geom_smooth(data=autismHI, method="lm") + facet_grid(cols = vars(SRS_VERSION)) + labs(title = "Autism", x = "Movement Score", y = "SRS Score") + theme(legend.position = "none")
```

Taking meds and balance subscores largely uninteresting except for typically developing balance subscore 3.

Taking Medication

```{r fig.width=4.2,fig.height=1.8}
# Not added to final presentation
adhdMedsYes <- filter(adhd, CurrentlyNotTakingMeds==FALSE)

adhdMedsNo <- filter(adhd, CurrentlyNotTakingMeds==TRUE)

medYesSummary <- summary(adhdMedsYes$SRS_TotalRawScore)

medNoSummary <- summary(adhdMedsNo$SRS_TotalRawScore)

medPlot <- ggplot(adhd, aes(x=mABC_TotalStandardScore, y=SRS_TotalRawScore, color=CurrentlyNotTakingMeds)) + geom_point() + geom_jitter() + geom_smooth(data=adhdMedsYes, method="lm", color="cyan") + geom_smooth(data=adhdMedsNo, method="lm", color="red")
```

## Typically Developing Model

```{r warning=FALSE}
typ.subset <- subset(typ, select = c(SRS_TotalRawScore, mABC_AGE, mABC_TotalStandardScore, mABC_Balance.1.StandardScore, mABC_Balance.2.StandardScore, mABC_Balance.3.StandardScore, mABC_Balance.Component.StandardScore, mABC_ManualDexterity.1.StandardScore, mABC_ManualDexterity.2.StandardScore, mABC_ManualDexterity.3.StandardScore, mABC_ManualDexterity.Component.StandardScore, mABC_AimingAndCatching.1.StandardScore, mABC_AimingAndCatching.2.StandardScore, mABC_AimingAndCatching.Component.StandardScore))

typCorrelations <- cor(typ.subset)


# Model with social score versus only movement score
withoutOthers <- summary(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore, typ))


# SRS Version


# Residuals to be used in added variable plot
typ.subset$SRSres <- residuals(lm(SRS_TotalRawScore ~ SRS_VERSION, data = typ))
typ.subset$mABCres <- residuals(lm(mABC_TotalStandardScore ~ SRS_VERSION, data = typ))

# Original
originalTypPlot <- ggplot(typ, aes(mABC_TotalStandardScore, SRS_TotalRawScore)) + geom_point() + geom_jitter() + geom_smooth(method="lm") + geom_smooth()

# Added variable plot: SRS_VERSION
versionAddedPlot <- ggplot(typ.subset, aes(mABCres, SRSres)) + geom_point() + geom_jitter() + geom_smooth(method="lm") + geom_smooth()

# Model with added varible: SRS_VERSION
typSummary <- summary(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore + SRS_VERSION, typ))


# Age
# No interesting results for age, just checking if it affects anything


# Residuals to be used in added variable plot
typ.subset$SRSres2 <- residuals(lm(SRS_TotalRawScore ~ mABC_AGE, data = typ))
typ.subset$mABCres2 <- residuals(lm(mABC_TotalStandardScore ~ mABC_AGE, data = typ))

# Original
originalTypPlot <- ggplot(typ, aes(mABC_TotalStandardScore, SRS_TotalRawScore)) + geom_point() + geom_jitter() + geom_smooth(method="lm") + geom_smooth()

# Added variable plot: AGE
ageAddedPlot <- ggplot(typ.subset, aes(mABCres2, SRSres2)) + geom_point() + geom_jitter() + geom_smooth(method="lm") + geom_smooth()

# Model with added varible: AGE
ageSummary <- summary(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore + mABC_AGE, typ))
```

```{r echo=TRUE}
typModel <- lm(SRS_TotalRawScore ~ mABC_TotalStandardScore * SRS_VERSION - 1, typ)
```

```{r}
typModelWithInt <- lm(SRS_TotalRawScore ~ mABC_TotalStandardScore * SRS_VERSION, typ)

typModel1 <- lm(SRS_TotalRawScore ~ mABC_TotalStandardScore - 1, typ)

#names(anova(typModel, typModel1))
#anova(typModel, typModel1)
#names(summary(typModel))
#summary(typModel)
#summary(typModelWithInt)
#summary(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore, typ, SRS_VERSION == "1"))
#summary(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore, typ, SRS_VERSION == "2"))

sprintf("Adjusted R Squared: %s, F Test's P Value: %s", round(summary(typModelWithInt)$adj.r.squared * 1000) / 1000, round(anova(typModel, typModel1)$"Pr(>F)"[2] * 1000) / 1000)

typMovementBeta <- summary(typModel)$coefficients[1]

typMovementBetaUpper <- typMovementBeta + qt(0.975,df=summary(typModel)$df[2]) * summary(typModel)$coefficients[1,2]
typMovementBetaLower <- typMovementBeta - qt(0.975,df=summary(typModel)$df[2]) * summary(typModel)$coefficients[1,2]

typInteractionTerm <- summary(typModel)$coefficients[4]

typInteractionTermUpper <- typInteractionTerm + qt(0.975,df=summary(typModel)$df[2]) * summary(typModel)$coefficients[4,2]
typInteractionTermLower <- typInteractionTerm - qt(0.975,df=summary(typModel)$df[2]) * summary(typModel)$coefficients[4,2]

#typMovementBetaUpper
#typMovementBetaLower 
#typInteractionTermUpper
#typInteractionTermLower

#confint(typModel)

sprintf("Version 1 Beta Estimates: y = %s + %sx", round(summary(typModel)$coefficients[2] * 10) / 10, round(typMovementBeta * 1000) / 1000)

sprintf("Version 2 Beta Estimates: y = %s + %sx", round(summary(typModel)$coefficients[3] * 10) / 10, round((typMovementBeta + typInteractionTerm) * 1000) / 1000)

#summary(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore * SRS_VERSION - 1, typ))

#summary(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore + mABC_TotalStandardScore * SRS_VERSION - 1, typ))

```

```{r fig.height=3,fig.width=3}
residuals <- residuals(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore * SRS_VERSION, typ))

residualsV1 <- residuals(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore, typVer1))

residualsV2 <- residuals(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore, typVer2))

values <- fitted.values(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore * SRS_VERSION, typ))

valuesV1 <- fitted.values(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore, typVer1))

valuesV2 <- fitted.values(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore, typVer2))

# Normality
#qqnorm(residuals)
qqnorm(residualsV1)
qqnorm(residualsV2)
```

## Checking Assumptions

```{r fig.height=2.5,fig.width=4}
# Linearity
#ggplot(data=NULL, aes(values, residuals)) + geom_point() + geom_smooth(method="loess", formula = y ~ x)
ggplot(data=NULL, aes(valuesV1, residualsV1)) + geom_point() + geom_smooth(method="loess", formula = y ~ x)
ggplot(data=NULL, aes(valuesV2, residualsV2)) + geom_point() + geom_smooth(method="loess", formula = y ~ x)
```

```{r fig.height=2.5,fig.width=4}
# Homoskadasticity
#ggplot(data=NULL, aes(values, residuals^2)) + geom_point() + geom_smooth(method="loess", formula = y ~ x)
ggplot(data=NULL, aes(valuesV1, residualsV1^2)) + geom_point() + geom_smooth(method="loess", formula = y ~ x)
ggplot(data=NULL, aes(valuesV2, residualsV2^2)) + geom_point() + geom_smooth(method="loess", formula = y ~ x)

# It looks like test version 1's data fits the three assumptions quite a bit better than test version 2's data
```

## ADHD Model

```{r warning=FALSE}
adhd.subset <- subset(adhd, select = c(SRS_TotalRawScore, mABC_AGE, CurrentlyNotTakingMeds, SecondaryDiagnosis, ADHD_Subtype, mABC_TotalStandardScore))

# adhdPlotMatrix <- scatterplotMatrix(adhd.subset)


# Model with social score versus only movement score
adhdJustMovementSummary <- summary(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore, adhd))


# ADHD Subtype


# Residuals to be used in added variable plot
adhd.subset$SRSres <- residuals(lm(SRS_TotalRawScore ~ ADHD_Subtype, adhd))
adhd.subset$mABCres <- residuals(lm(mABC_TotalStandardScore ~ ADHD_Subtype, adhd))

# Original for comparison
originalADHDPlot <- ggplot(adhd, aes(mABC_TotalStandardScore, SRS_TotalRawScore)) + geom_point() + geom_jitter() + geom_smooth() + geom_smooth(method="lm")

# Added variable plot: ADHD_Subtype
subtypeAddedADHDPlot <- ggplot(adhd.subset, aes(mABCres, SRSres)) + geom_point() + geom_jitter() + geom_smooth() + geom_smooth(method="lm")

# Model with added varible: ADHD_Subtype
adhdSubtypeSummary <- summary(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore + ADHD_Subtype, adhd))


# Secondary Diagnosis


# Residuals to be used in added variable plot
adhd.subset$SRSres2 <- residuals(lm(SRS_TotalRawScore ~ SecondaryDiagnosis, adhd.subset))
adhd.subset$mABCres2 <- residuals(lm(mABC_TotalStandardScore ~ SecondaryDiagnosis, adhd))

# Original for comparison
originalADHDPlot <- ggplot(adhd, aes(mABC_TotalStandardScore, SRS_TotalRawScore)) + geom_point() + geom_jitter() + geom_smooth() + geom_smooth(method="lm")

# Added variable plot: SecondaryDiagnosis
secondaryDiagnosisAddedADHDPlot <- ggplot(adhd.subset, aes(mABCres2, SRSres2)) + geom_point() + geom_jitter() + geom_smooth() + geom_smooth(method="lm")

# Model with added varible: SecondaryDiagnosis
adhdSecondaryDiagnosisSummary <- summary(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore + SecondaryDiagnosis, adhd))


# F Tests

adhdJustMovementSummary <- summary(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore - 1, adhd))

adhd <- filter(adhd, !(is.na(CurrentlyNotTakingMeds)))

adhdModel1 <- lm(SRS_TotalRawScore ~ mABC_TotalStandardScore, adhd)

adhdModel2 <- lm(SRS_TotalRawScore ~ mABC_TotalStandardScore * SRS_VERSION - 1, adhd)

adhdModel3 <- lm(SRS_TotalRawScore ~ mABC_TotalStandardScore * SRS_VERSION + SecondaryDiagnosis - 1, adhd)

adhdModel4 <- lm(SRS_TotalRawScore ~ mABC_TotalStandardScore * SRS_VERSION + SecondaryDiagnosis + ADHD_Subtype +  CurrentlyNotTakingMeds - 1, adhd)

#Comment out because p value of CurrentlyNotTakingMeds was too high to include it
#This was also true when comparing just adding CurreentlyNotTakingMedsand comparing to baseline model

```

```{r echo=TRUE}
adhdModel <- lm(SRS_TotalRawScore ~ mABC_TotalStandardScore * SRS_VERSION 
                + SecondaryDiagnosis + ADHD_Subtype - 1, adhd)
```

```{r}
adhdModelWithInt <- lm(SRS_TotalRawScore ~ mABC_TotalStandardScore * SRS_VERSION + SecondaryDiagnosis + ADHD_Subtype, adhd)

addingSecondaryDiagnosisSignificance <- anova(adhdModel2, adhdModel1)$"Pr(>F)"[2]

addingSubtypeSignificance <- anova(adhdModel3, adhdModel2)$"Pr(>F)"[2]

addingVersionSignificance <- anova(adhdModel4, adhdModel3)$"Pr(>F)"[2]

#names(anova(adhdModel, adhdModel3))
#anova(adhdModel, adhdModel3)
#names(summary(adhdModel))
#summary(adhdModel)
summary(adhdModelWithInt)
#summary(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore + SecondaryDiagnosis + ADHD_Subtype, adhd, SRS_VERSION == "1"))
#summary(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore + SecondaryDiagnosis + ADHD_Subtype, adhd, SRS_VERSION == "2"))

sprintf("Adjusted R Squared: %s, F Test's P Value: %s, For Taking Meds: %s", round(summary(adhdModelWithInt)$adj.r.squared * 1000) / 1000, round(anova(adhdModel, adhdModel3)$"Pr(>F)"[2] * 1000) / 1000, round(anova(adhdModel4, adhdModel)$"Pr(>F)"[2] * 1000) / 1000)

adhdMovementBeta <- summary(adhdModel)$coefficients[1]

adhdMovementBetaUpper <- adhdMovementBeta + qt(0.975,df=summary(adhdModel)$df[2]) * summary(adhdModel)$coefficients[1,2]
adhdMovementBetaLower <- adhdMovementBeta - qt(0.975,df=summary(adhdModel)$df[2]) * summary(adhdModel)$coefficients[1,2]

adhdInteractionTerm <- summary(adhdModel)$coefficients[7]

adhdInteractionTermUpper <- adhdInteractionTerm + qt(0.975,df=summary(adhdModel)$df[2]) * summary(adhdModel)$coefficients[7,2]
adhdInteractionTermLower <- adhdInteractionTerm - qt(0.975,df=summary(adhdModel)$df[2]) * summary(adhdModel)$coefficients[7,2]

#adhdMovementBetaUpper
#adhdMovementBetaLower
#adhdInteractionTermUpper
#adhdInteractionTermLower

#confint(adhdModel)

sprintf("Version 1 Beta Estimates: y = %s + %sx", round(summary(adhdModel)$coefficients[2] * 10) / 10, round(adhdMovementBeta * 1000) / 1000)

sprintf("Version 2 Beta Estimates: y = %s + %sx", round(summary(adhdModel)$coefficients[3] * 10) / 10, round((adhdMovementBeta + adhdInteractionTerm) * 1000) / 1000)
```

```{r fig.height=3,fig.width=3}
residuals <- residuals(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore * SRS_VERSION + SecondaryDiagnosis + ADHD_Subtype, adhd))

residualsV1 <- residuals(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore + SecondaryDiagnosis + ADHD_Subtype, adhdVer1))

residualsV2 <- residuals(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore + SecondaryDiagnosis + ADHD_Subtype, adhdVer2))

values <- fitted.values(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore * SRS_VERSION + SecondaryDiagnosis + ADHD_Subtype, adhd))

valuesV1 <- fitted.values(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore + SecondaryDiagnosis + ADHD_Subtype, adhdVer1))

valuesV2 <- fitted.values(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore + SecondaryDiagnosis + ADHD_Subtype, adhdVer2))

# Normality
#qqnorm(residuals)
qqnorm(residualsV1)
qqnorm(residualsV2)
```

## Checking Assumptions

```{r fig.height=2.5,fig.width=4}
# Linearity
#ggplot(data=NULL, aes(values, residuals)) + geom_point() + geom_smooth(method="loess", formula = y ~ x)
ggplot(data=NULL, aes(valuesV1, residualsV1)) + geom_point() + geom_smooth(method="loess", formula = y ~ x)
ggplot(data=NULL, aes(valuesV2, residualsV2)) + geom_point() + geom_smooth(method="loess", formula = y ~ x)
```

```{r fig.height=2.5,fig.width=4}
# Homoskadasticity
#ggplot(data=NULL, aes(values, residuals^2)) + geom_point() + geom_smooth(method=loess", formula = y ~ x)
ggplot(data=NULL, aes(valuesV1, residualsV1^2)) + geom_point() + geom_smooth(method="loess", formula = y ~ x)
ggplot(data=NULL, aes(valuesV2, residualsV2^2)) + geom_point() + geom_smooth(method="loess", formula = y ~ x)

# It looks like test version 1's data fits the three assumptions quite a bit better than test version 2's data
```

## Autism Model

```{r}
autismJustMovementSummary <- summary(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore, autism))

autism <- filter(autism, !(is.na(CurrentlyNotTakingMeds)))

#autism <- filter(autism, !(is.na(ADHD_Subtype)))
```

```{r echo=TRUE}
autismModel <- lm(SRS_TotalRawScore ~ mABC_TotalStandardScore * SRS_VERSION 
                  + SecondaryDiagnosis - 1, autismWithSecond)
```

```{r}
autismModelWithInt <- lm(SRS_TotalRawScore ~ mABC_TotalStandardScore * SRS_VERSION + SecondaryDiagnosis, autismWithSecond)

autismModel1 <- lm(SRS_TotalRawScore ~ mABC_TotalStandardScore * SRS_VERSION, autismWithSecond)

#autismModel4 <- lm(SRS_TotalRawScore ~ mABC_TotalStandardScore * SRS_VERSION +SecondaryDiagnosis + CurrentlyNotTakingMeds, autismWithSecond)

#names(anova(autismModel, autismModel1))
#anova(autismModel, autismModel1)
#names(summary(autismModel))
#summary(autismModel)
#summary(autismModelWithInt)
#summary(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore + SecondaryDiagnosis - 1, autismWithSecond, SRS_VERSION == "1"))
#summary(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore + SecondaryDiagnosis - 1, autismWithSecond, SRS_VERSION == "2"))

sprintf("Adjusted R Squared: %s, F Test's P Value: %s", round(summary(autismModelWithInt)$adj.r.squared * 1000) / 1000, round(anova(autismModel,autismModel1)$"Pr(>F)"[2] * 1000) / 1000)

autismMovementBeta <- summary(autismModel)$coefficients[1]

autismMovementBetaUpper <- autismMovementBeta + qt(0.975,df=summary(autismModel)$df[2]) * summary(autismModel)$coefficients[1,2]
autismMovementBetaLower <- autismMovementBeta - qt(0.975,df=summary(autismModel)$df[2]) * summary(autismModel)$coefficients[1,2]

autismInteractionTerm <- summary(autismModel)$coefficients[6]

autismInteractionTermUpper <- autismInteractionTerm + qt(0.975,df=summary(autismModel)$df[2]) * summary(autismModel)$coefficients[6,2]
autismInteractionTermLower <- autismInteractionTerm - qt(0.975,df=summary(autismModel)$df[2]) * summary(autismModel)$coefficients[6,2]

#autismMovementBetaUpper
#autismMovementBetaLower
#autismInteractionTermUpper
#autismInteractionTermLower

#confint(autismModel)

sprintf("Version 1 Beta Estimates: y = %s + %sx", round(summary(autismModel)$coefficients[2] * 10) / 10, round(autismMovementBeta * 100) / 100)

sprintf("Version 2 Beta Estimates: y = %s + %sx", round(summary(autismModel)$coefficients[3] * 10) / 10, round((autismMovementBeta + autismInteractionTerm) * 1000) / 1000)
```

```{r}
#autismModel3 <- lm(SRS_TotalRawScore ~ mABC_TotalStandardScore + SRS_VERSION + ADHD_Subtype, autism)
#autismModel4 <- lm(SRS_TotalRawScore ~ mABC_TotalStandardScore + SRS_VERSION + ADHD_Subtype + SecondaryDiagnosis, autism)
#autismModel5 <- lm(SRS_TotalRawScore ~ mABC_TotalStandardScore +  SRS_VERSION + CurrentlyNotTakingMeds, autism)
#Comment out because p values of variables were too high to include them

#anova(autismModel3, autismModel2)
#anova(autismModel4, autismModel3)
#anova(autismModel5, autismModel4)
```

```{r fig.height=3,fig.width=3}
residuals <- residuals(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore * SRS_VERSION + SecondaryDiagnosis, autism))

residualsV1 <- residuals(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore + SecondaryDiagnosis, autismVer1))

residualsV2 <- residuals(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore + SecondaryDiagnosis, autismVer2))

values <- fitted.values(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore * SRS_VERSION + SecondaryDiagnosis, autism))

valuesV1 <- fitted.values(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore + SecondaryDiagnosis, autismVer1))

valuesV2 <- fitted.values(lm(SRS_TotalRawScore ~ mABC_TotalStandardScore + SecondaryDiagnosis, autismVer2))

# Normality
#qqnorm(residuals)
qqnorm(residualsV1)
qqnorm(residualsV2)
```

## Checking Assumptions

```{r fig.height=2.5,fig.width=4}
# Linearity
#ggplot(data=NULL, aes(values, residuals)) + geom_point() + geom_smooth(method="loess", formula = y ~ x)
ggplot(data=NULL, aes(valuesV1, residualsV1)) + geom_point() + geom_smooth(method="loess", formula = y ~ x)
ggplot(data=NULL, aes(valuesV2, residualsV2)) + geom_point() + geom_smooth(method="loess", formula = y ~ x)
```

```{r fig.height=2.5,fig.width=4}
# Homoskadasticity
#ggplot(data=NULL, aes(values, residuals^2)) + geom_point() + geom_smooth(method="loess", formula = y ~ x)
ggplot(data=NULL, aes(valuesV1, residualsV1^2)) + geom_point() + geom_smooth(method="loess", formula = y ~ x)
ggplot(data=NULL, aes(valuesV2, residualsV2^2)) + geom_point() + geom_smooth(method="loess", formula = y ~ x)

# It looks like test version 1's data fits the three assumptions quite a bit better than test version 2's data
```

## Comparing Beta Estimates

```{r}
#summary(data)
#names(data)

betas <- data.frame(
   DiagnosisGroup = factor(c("_Typ1","_Typ2","Adhd1","Adhd2","Autism1","Autism2")),
   BetaEstimates = c(typMovementBeta, typMovementBeta + typInteractionTerm,adhdMovementBeta,adhdMovementBeta + adhdInteractionTerm,autismMovementBeta,autismMovementBeta + autismInteractionTerm),
   Version = factor(c(1,2,1,2,1,2)),
   upper = c(typMovementBetaUpper,typMovementBeta + typInteractionTermUpper,adhdMovementBetaUpper,adhdMovementBeta + adhdInteractionTermUpper,autismMovementBetaUpper,autismMovementBeta + autismInteractionTermUpper),
   lower = c(typMovementBetaLower,typMovementBeta + typInteractionTermLower,adhdMovementBetaLower,adhdMovementBeta + adhdInteractionTermLower,autismMovementBetaLower,autismMovementBeta + autismInteractionTermLower)
)

ggplot(betas, aes(DiagnosisGroup, BetaEstimates, color = Version)) + geom_pointrange(aes(ymin = lower, ymax = upper))

```
